\chapter{Introduction}
Key Word Spotting is the task of identifying spoken words from human speakers out of a limited vocabulary or set of Key Words, e.g. identify the word \enquote{left} out of the vocabulary \{\enquote{left}, \enquote{right}\}. This problem is easily solved by humans in everyday live, but it is a real challenge for computer systems on which we aim to tackle it.

One approach to solve Key Word Spotting on a computer system is to use the advances of Machine Learning. which enables the computer to automatically learn abstract representations of the data given as input. 
The output of a Machine Learning system is...
and to infer an appropriate output, e.g. the waveform of \enquote{left} stored as \textit{.mp4} file is

Nowadays there are already many existing applications in the real world accessible for consumers (e.g. \textit{Alexa} from the company \textit{Amazon}).

While the task of Key Word Spotting is not a new one, it is solved with a variety of different approaches. One approach commonly used in recent times, is a Machine Learning system composed of a Neural Networks. The big advantage of Neural Networks is that they are able to learn how to process features in an automatic fashion, which means, that they learn their own feature extractions, selection and interpretation by themselves, rather than using hand-crafted ones done by humans with expertise in the application. 
What sound great at first hand, is also a bit of a downfall, as everyone who is able to use Machine Learning tools, can create a solution to rather complex problem usually done by experts, given they have enough data and processing power.
This solution concept therefore yield into less understanding of the actual problem and \enquote{try and error} approaches. However it is not always this way, certainly we can investigate how and why Neural Networks are able to produce such good results and therefore we might learn more on the field of expertise.

%However unfortunately due to the (usually) large amount of data and complex Neural Network Architectures it is in most cases not tractable, how these systems learn to distinguish between different samples. Nevertheless the technical benefits and their performance made them a standard tool in modern Machine Learning tasks.

\input{./1_intro/a_kws}
\input{./1_intro/b_neural_nets}
\input{./1_intro/c_video_games}
\newpage
\input{./1_intro/d_problem_formulation}
\input{./1_intro/d1_signal_processing}
\input{./1_intro/d2_neural_net}
\input{./1_intro/d3_game}

\input{./1_intro/e_visual_guidance}



