% --
% game interactables

\section{Game Elements}
\thesisStateNotReady
In this section the game elements for the deployed KWS video game are presented.


% --
% menu

\subsection{Menu}\label{sec:game_interactables_menu}
The game menu is the first screen that appears, when starting a video game. 
It usually consists of selectable buttons referencing for instance the game setting of graphic and music.
With speech input deployed in a video game, the setting of the recording device is useful to be added.
All available microphone input devices should be visualized in a list and being selectable to switch between the devices.
Further a small visualization bar of the input signals energy from the selected device is beneficial, so that the user can verify its correct functionality.
An option for adjusting the energy threshold, by which the device detects the onset of a speech signal, must be added if this property is used within the video game.
The threshold must be adjustable because of varying recording amplification factors in different microphone set ups.


% --
% game mechanics

\subsection{Game Mechanics}
The game mechanics with KWS are a highly time restricted, because of the processing time of the speech signals.
In this thesis the KWS system was used as augmented input control.
With standard control keys on the keyboard the controlling of the character is handled, to receive immediate feedback for the player. 
For other more special tasks that do not require immediate feedback, the KWS control were applied.

One game mechanic possibility is to move game objects... 



